---
title: "popularplays"
author: "Alexis Santise"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
First, set up a Dev account with Spotify to access their Web API [here](https://developer.spotify.com/dashboard/). This will give you your Access Token (<code>Client ID</code> and <code>Client Secret</code>) that you will input into the function.

This README is derived from Charlie Thompson's excellent [spotifyr](https://www.rcharlie.com/spotifyr/) documentation.

## Install

Install from GitHub with the following code:

```{r install, eval = FALSE}
if (!requireNamespace("devtools", quietly = TRUE)) {
  install.packages("devtools")
}
devtools::install_github("lexisantise/popularplays")
```

This package uses your <code>Access Token</code> and <code>spotifyr</code> to pull the last songs you have played on Spotfiy and give you a visual of how popular each song is based on Spotify's current records.

## Usage

There is one function currently live for popularplay. 

To use, the user must enter the following code, inserting their <code>Client ID</code>, <code>Client Secret</code> where appropriate:

```{setup instructions, eval = FALSE}
PopularPlays("XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX",
"XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX")
```

When you run the code, you will be asked if you want to:
"Use a local file ('.httr-oauth'), to cache 0Auth access credentials between R sessions?
1. Yes
2. No

In your console, enter the following code when prompted:
```{prompt1, eval = FALSE}
Selection: 1
```

You will then be asked to:
"Enter an item from the menu, or 0 to exit"
In your console, enter the following code when prompted:
```{prompt2, eval = FALSE}
Selection: 0
```


You will then see a bar graph of the Last 20 Songs Played by Popularity. The y-axis is the title of the last 20 songs you have played. The X-Axis is a sccale of popularity based on Spotify's current records from 0-100(0 being least popular, 100 being most popular. You can compare each song's popularity by looking at the length and color of the bars. The lighter the green, the more popular. The darker the green, the less popular.

From this graph, you can learn about your listening habits. If you tend listen to new releases from big artists, or the top charts playlists that Spotify offers, your bar graph may be consistently long on the x-axis. If you tend to listen to older music, the popularity scores of your songs may be consistently lower. If you listen to both spectrums, your bars may be sporadic in popularity.

