---
title: "popularplays"
author: "Alexis Santise"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
This package pulls the last songs the user has played on Spotfiy
and gives a visual of how popular each song is based on Spotify’s
current records

This README is derived from Charlie Thompson's excellent [spotifyr](https://www.rcharlie.com/spotifyr/) documentation.

## Install

Install from GitHub with the following code:

```{r install, eval = FALSE}
if (!requireNamespace("devtools", quietly = TRUE)) {
  install.packages("devtools")
}
devtools::install_github("lexisantise/popularplays")
```

This package uses the user's <code>Access Token</code> and
<code>spotifyr</code> to pull the last songs played and returns a visual of the
popularity of each song.

## Usage

First, set up a Dev account with Spotify to access their Web API
[here](https://developer.spotify.com/dashboard/). This will give the user an
Access Token (<code>Client ID</code> and <code>Client
Secret</code>) that the user will input into the function.

There is one function currently live for popularplay. 

To use, the user must enter the following code, inserting their <code>Client ID</code>, <code>Client Secret</code> where appropriate:

```{setup instructions, eval = FALSE}
PopularPlays("XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX",
"XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX")

or

PopularPlays(Client_ID = "XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX",
Client_Secret = "XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX")
```

When the user runs the code, they will be asked if they want to:
"Use a local file ('.httr-oauth'), to cache 0Auth access credentials between R sessions?
1. Yes
2. No

In the console, enter the following code when prompted:
```{prompt1, eval = FALSE}
Selection: 1
```

The user will then be asked to:
"Enter an item from the menu, or 0 to exit"
In the console, enter the following code when prompted:
```{prompt2, eval = FALSE}
Selection: 0
```


The user will then see a bar graph of the Last 20 Songs Played by Popularity.
The y-axis is the title of the last 20 songs the user has played. The X-Axis
is a scale of popularity based on Spotify’s current records from
0-100 (0 being least popular, 100 being most popular). The user can compare
each song’s popularity by looking at the length and color of the bars.
The lighter the green, the more popular. The darker the green, the less
popular.

From this graph, the user can learn about their listening habits. If the user tends to
listen to new releases from big artists, or the top charts playlists
that Spotify offers, the bar graph may be consistently long on the
x-axis. If the user tends to listen to older music, the popularity scores of
the songs may be consistently lower. If the user listens to both spectrums,
the bars may be sporadic in popularity.

